### 2023-01-31 manuscript.tex
now using biblatex [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/a78fcc264323c8aac5b5620d946ef6d07686c498.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/a78fcc264323c8aac5b5620d946ef6d07686c498/checks
https://github.com/stain/2022-fdo-paper/actions/runs/4055058960

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/bfaaab005d18e6d1a45e17f5adbda0cf18649697/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/bfaaab005d18e6d1a45e17f5adbda0cf18649697}{stain/2022-fdo-paper@bfaaab0}
on January 31, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/a78fcc264323c8aac5b5620d946ef6d07686c498/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/a78fcc264323c8aac5b5620d946ef6d07686c498}{stain/2022-fdo-paper@a78fcc2}
on January 31, 2023.
